---
title: "Superhost"
author: "Han Zhang"
date: "12/3/2021"
output:  
   pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## **Superhost Model**
## *logsitic regression*
*Superhost* are experienced hosts who provide a shining example for other hosts, and extraordinary experiences for their guests. Once they are called Superhosts, and their listings feature a special badge that let everyone know they are extra awesome. Althoug the airbnb websites have posted out the standards of becoming a superhost. We still want to dig out important information from the data analysis, and then provide evey host with insights about how to increase the probability of becoming a superhost. 
```{r echo= FALSE }
library(readr)
library(tidyverse)
listingdata = read.csv('F:/bios625/project/ny/listings.csv')

interest_variable = c("host_id", "host_response_time","host_response_rate","host_is_superhost","bathrooms_text","amenities","room_type",
                       "host_identity_verified","accommodates","bedrooms","price","number_of_reviews","review_scores_rating",
                      "instant_bookable" ,"reviews_per_month","review_scores_cleanliness","review_scores_accuracy" ,"review_scores_checkin" ,"review_scores_communication")

hostdata = select(listingdata,all_of(interest_variable))

```


```{r echo=FALSE, warning=FALSE}
#hostdata = read.csv('host_data_without_comments_NYC.csv')
#omit the na rows
hostdata[hostdata=="N/A"] = NA
hostdata2 = na.omit(hostdata)
#filter out the empty rows
hostdata3 = hostdata2[!apply(hostdata2 == "", 1, any),]
#change text bathroom into number
bathroom_n = readr::parse_number(hostdata3$bathrooms_text, na = 'NA')
hostdata3$bathroom_n = bathroom_n
#change the price text into number
price = readr::parse_number(hostdata3$price, na = "NA")
hostdata3$price_n = price
#change the host_response_time into factor variables
hostdata3 <- hostdata3 %>% mutate(hs_response_time = case_when(
  host_response_time == "within an hour" ~ 1L,
  host_response_time =="within a few hours" ~ 2L,
  host_response_time =="within a day" ~ 3L,
  TRUE ~ 4L
))

# change response_rate into number
hs_response_rate = readr::parse_number(hostdata3$host_response_rate)/100
hostdata3$hs_response_rate =hs_response_rate

#change accepetance _rate into number
# hs_accepetance_rate =  readr::parse_number(hostdata3$host_acceptance_rate)/100
# hostdata3$hs_accepetance_rate = hs_accepetance_rate

# change instant_bookable into 0, 1
hostdata3$instant_bookable = ifelse(hostdata3$instant_bookable=="t",1,0)
hostdata3$host_is_superhost = ifelse(hostdata3$host_is_superhost=="t",1,0)
hostdata3$host_identity_verified = ifelse(hostdata3$host_identity_verified=="t",1,0)

hostdata4 = na.omit(hostdata3)
```
##
The _host_is_superhost_ is a binary varaible, which takes the values of "True" or "Flase". Thus, we use logistic regression to build our model. And We select _14_ variables which is potentially related to the superhost. After excluding missing data, we ended up with 14,058 obsersvations. We didn't include the _comments_ and _ammenities_ varaibles, which are text information and will be analyazed by different model. 

First, we tested the correlation between covariates, and found that there existed high correlationship among same prefix variables. Since these variables contain different underlying information, we use *Principle Component Analysis* (PCA) to overcome the multicollinearity problem and extracting dominant patterns in a group of predictor.

We randomly split the observations into training set and test set at a ratio of 7:3. Since we didn't know which varaibles should be selected, we dumped all varaibles into the regression model, and filtered out the appropriates variables according to the real situation and  **Akaike information criterion** (AIC).


```{r echo= FALSE}
#only covariates
covariates = hostdata4[,c("host_identity_verified","accommodates","bedrooms","number_of_reviews","instant_bookable" ,"reviews_per_month","review_scores_cleanliness",   "review_scores_accuracy",      "review_scores_checkin","review_scores_communication", "bathroom_n" , "price_n","hs_response_time",            "hs_response_rate" )]

library("corrplot")
mycor = corrplot(cor(covariates))

#full components pca
fullpca = princomp(covariates,cor = T)
fullpca_pred = predict(fullpca)


#review principal components
reviewpca = princomp(data.frame(hostdata4$review_scores_cleanliness,hostdata4$review_scores_accuracy
                                , hostdata4$review_scores_checkin,hostdata4$review_scores_communication),cor =T)
reviewpca_pred = predict(reviewpca)

#response  principal components
responsepca = princomp(data.frame(hostdata4$hs_response_rate,hostdata4$hs_response_time))
responsepca_pred = predict(responsepca)

# bedroom bathroom accommodates principal components
bbpca = princomp(data.frame(hostdata4$accommodates,hostdata4$bedrooms,hostdata4$bathroom_n,hostdata4$price_n))
bbpca_pred = predict(bbpca)

#all covariates are used in the log regression auc = 0.7646
library(Deducer)
logistic0 = glm(hostdata4$host_is_superhost ~., data = covariates)
logistsic0_reg= step(logistic0,direction = 'back')
rocplot(logistsic0_reg)

# use the principal components of reviews and response and bed/bath auc = 0.7644
xx = data.frame(covariates[,c("host_identity_verified","number_of_reviews" ,"instant_bookable","reviews_per_month")],reviewpca_pred,responsepca_pred,bbpca_pred)
logistic1 = glm(hostdata4$host_is_superhost ~., data = xx)
logistsic1_reg= step(logistic1,direction = 'back')
rocplot(logistsic1_reg)

# conduct the pca with whole covariates auc= 0.7646
logistic2 = glm(hostdata4$host_is_superhost ~., data = data.frame(fullpca_pred))
logistsic2_reg= step(logistic2,direction = 'back')
rocplot(logistsic2_reg)

```

Finally, we attained a "superhost" model. And then we apply this pre-trained model to the test case. The **Area Under the Curve** (AUC) is 0.776, meaning our model can effectively distinguish the superhost and nonsuperhost classes. 

When getting inside into the model, we find that _hs_response_rate_ and _hs_response_time_ contribute a lot to the model from the magnitude of the coeffecient. So we assume that improving the response rate and shrinking the response time may increase the chance of becoming a superhost.

```{r echo=FALSE, warning=FALSE}
# test train

set.seed(100)

samplet = sample(c(1:nrow(hostdata4)), as.integer(nrow(hostdata4))*3/10)
tesths = covariates[samplet,]
trainhs = covariates[-samplet,]

#train set regression
logistic3 = glm(hostdata4[-samplet,"host_is_superhost"]~. , data = trainhs)
logistsic3_reg= step(logistic3,direction = 'back')
rocplot(logistsic3_reg)
summary(logistsic3_reg)

prediction = predict(logistsic3_reg,type = "response", newdata = tesths)
library("pROC")
modelroc = roc(hostdata4[samplet,"host_is_superhost"],prediction)
plot(modelroc, print.auc=T)

```

## *Associating Rule Mining*

The _ammenities_ is a text variable, cantaining a list of ammenities of the house or department. We assume that there are some association between the availability of certain ammenities and the superhost. In order to dig out the information behind the sets of items, we borrow the algorithm *Association Rule* from business field. Given a set of data, we can find the rules that will predict the occurrence of superhost based on the occurrences of ammenities in the list.
```{r echo=FALSE, warning=FALSE}
library(stringr)
library(arules)
library(leaflet)
library(fpc)
library(openxlsx)
library(ggplot2)
c = hostdata4[1:nrow(hostdata4),"amenities"]
for(i in 1:nrow(hostdata4)){
  c[i] = gsub('"','',substr(c[i],2,nchar(c[i])-1))
  c[i]=str_replace(c[[i]],', [^,]*TV with [^,]*(,)|, [^,]*TV with [^,]*[a-zA-Z]$',', TV\\1')
  c[i]=str_replace(c[[i]],', [^,]*[sS]ound system[^,]*(,)|, [^,]*[sS]ound system[^,]*[a-zA-Z]$',', Sound system\\1')
  c[i]=str_replace(c[[i]],', [^,]*refrigerator ^,]*(,)|, [^,]*refrigerator[^,]*[a-zA-Z]$',', Refrigerator\\1')
  c[i]=str_replace(c[[i]],', [^,]*[Gg]ame console[^,]*(,)|, [^,]*[Gg]ame console [^,]*[a-zA-Z]$',', Game console\\1')
  c[i]=str_replace(c[[i]],', [^,]*[Ff]ree[^,]*parking[^,]*(,)|, [^,]*[Ff]ree[^,]*parking[^,]*[a-zA-Z]$',', Free parking\\1')

}

d = hostdata4[1:nrow(hostdata4),"host_is_superhost"]
for (i in 1:nrow(hostdata4)){
  if (d[i] == 1) {
    c[i] = paste(c[i]," superhost", sep = ',')
  } else {
    c[i] = paste(c[i]," non_superhost",sep = ',')
  }
}
write.csv2(c,'c.csv',row.names =F, quote = F )

basket2 = read.transactions('c.csv',format ='basket',sep=',')
itemFrequencyPlot(basket2,topN=10,horiz =T,col='red')
# rules2=apriori(basket2,parameter = list(support = 0.5, confidence = 0.8, maxlen = 10,minlen=5))
# #remove duplicate set
# subset.rules <- which(colSums(is.subset(rules2, rules2)) > 1)
# plotly_arules(subRules)
```

We use *Apriori Algorithm* to generate asscocaition rules from the ammenities and superhost. The Apriori algorithm employs level-wise search for frequent itemsets. It works by eliminating itemsets by looking ï¬rst at smaller sets and recognizing that a large set cannot be frequent unless all its subsets are. Put simply, the algorithm states that if an itemset is infrequent, then all its subsets must also be infrequent. 

* X:$X$ is called antecedent or left-hand-side (LHS).
* Y:$Y$ is called consequent or right-hand-side (RHS)

* Support: The frequency of A in the dataset.
  $Supp(X) = \frac{Freq(X)}{T}$
  
* Confidence: How often the items X and Y occur together in the dataset when the occurence of X is already given.
  $Confidence = \frac{Freq(X,Y)}{Freq(X)}$
  
* Lift: The ratio of the observed support measure and expected support if X and Y are independent of each other. 
  $Lift=\frac{Supp(X,Y)}{{Supp(X)}\times{Supp(X)}}$
  * $Lift=1$ : The probability of occurrence of antecedent and consequent is independent of each other.
  * $Lift>1$ : It determines the degree to which the two itemsets are dependent to each other.
  * $Lift<1$ :  It tells us that one item is a substitute for other items, which means one item has a negative effect on another.
  
In the ammenities, there are over 1400 items. In order to find what ammenities sets appear most frequently given that the host is a superhost, we set the maximum length of rules to 10, and limit the confidence level to 0.8, and then rank the rules by lift in descending order.

Finally, we find that if the apartment has building staff and conditioner, the host is likely to be a superhost.

```{r}
# plotly_arules(subRules)

library(arulesViz)
association.rules <- apriori(basket2, parameter = list(supp=0.01, conf=0.8, maxlen =10),
                             appearance = list(default="lhs",rhs="superhost"))
subset.rules <- which(colSums(is.subset(association.rules, association.rules)) > 1)
#length(association.rules)
#length(subset.rules)
reduced_rule = association.rules[-subset.rules]
fre = sort(reduced_rule,by='lift',decreasing =T)
#inspect(fre)
plot(fre)
#plot_arules(fre)
plot(fre, method = "graph",  engine = "htmlwidget")
plot(fre, method="paracoord")

association.rules2 <- apriori(basket2, parameter = list(supp=0.2, conf=0.8, maxlen = 10,minlen=5),
                             appearance = list(default="lhs",rhs="non_superhost"))

fre2 = sort(association.rules2,by='lift',decreasing =T)
#inspect(head(fre2,n=10))

```

##Comments
```{r echo=FALSE}
comments = read_csv("F:/bios625/project/reviews.csv")
```

1. Cleaning and Removing Noise
First we get rid of unhelpful parts of the data, or noise, by converting characters to lowercase, removing punctuations marks, and removing stop words and typos.
2. Convert the Format
We convert the txt format of comments into CSV in order to facilitate reading and manipulate the data
3. Feature Extraction
We use the most popular feature extraction techniques, TfidfVectorizer and CountVectorizer for text data. CountVectorizer converts a collection of text documents to a matrix of token counts: the occurrences of tokens in each document. This implementation produces a sparse representation of the counts. TfidfVectorizer weights the word counts by a measure of how often they appear in the documents. The reason why we use these two feature extraction technique is that we want to compare the pro and cons of these two techniques under the current dataset.
4. Model Fitting
We try to fit the extracted features (comments) with corresponding lables(superhost), by employing several machine learning models, including _Logistic Regression_, _Naive Bayesian_, _Random forest_, and _XGBoost_. We first send models to the training split to learn, and then validate them in the tesing splits. When evaluating and comparing the performance of the models, we use *accuracy*, *call*, and *F1* .etc


## Tables for ML
```{r message=FALSE, warning=FALSE}
# install.packages("kableExtra")
library(kableExtra)
options(knitr.kable.NA='')
TFIDF = readxl::read_excel("F:/bios625/project/bios625_fp/other/TFIDF.xlsx")
# t1 = TFIDF %>% kbl(caption = "The results of ML models based on TfidfVectorizer") %>% kable_classic_2(full_width = F) 
CountV = readxl::read_excel("F:/bios625/project/bios625_fp/other/CountVectorizer.xlsx")
# t2 = TFIDF %>% kbl(caption = "The results of ML models based on CountVectorizer") %>% kable_classic_2(full_width = F) 
# knitr::kables(list(knitr::kable(TFIDF,caption ="The results of ML models based on TfidfVectorizer" ), knitr::kable(CountV,caption ="The results of ML models based on CountVectorizer" )))
# kable(TFIDF) %>%
#   kable_styling(full_width = FALSE, position = "float_left")
# kable(CountV ) %>%
#   kable_styling(full_width = FALSE, position = "left")

knitr::kables(list(
  kable(caption = "The results of ML models based on TfidfVectorizer",
    TFIDF
    ) %>% kable_styling(),
    kable(caption = "The results of ML models based on CountVectorizer",
      CountV
    ) %>% kable_styling()
    
  )
) %>% kable_styling()

```

